---
title: "3 · Analysis"
subtitle: "Main effect, mediation, and moderation"
date: today
---

```{r setup}
#| include: false
source(file.path(rprojroot::find_root(rprojroot::is_git_root), "R", "01_setup.R"))
clean <- get_clean_consumer_data()
```

Three questions, three models — all defined once in
[`R/functions/analysis.R`](https://github.com/TheDataFlowCompany/the-science-repository/blob/main/R/functions/analysis.R)
and reused by the [manuscript](https://github.com/TheDataFlowCompany/the-science-repository/tree/main/reports/manuscript).

## Main effect: does the frame move purchase intention?

```{r}
#| label: tbl-main
#| tbl-cap: "Main model: condition predicting purchase intention (with covariates)."
fit_main <- fit_main_model(clean)
knitr::kable(broom::tidy(fit_main, conf.int = TRUE), digits = 3)
```

The `combined_frame` coefficient is the one to watch — a clear bump over the
`control` reference.

## Mediation: does perceived value carry the effect?

Three regressions tell the conceptual mediation story [@baron1986; @hayes2017]:

```{r}
#| label: tbl-mediation
med <- fit_mediation_models(clean)
dplyr::bind_rows(
  total       = broom::tidy(med$total, conf.int = TRUE),
  mediator    = broom::tidy(med$a,     conf.int = TRUE),
  outcome_w_m = broom::tidy(med$b,     conf.int = TRUE),
  .id = "model"
) |>
  dplyr::filter(grepl("condition|perceived_value", term)) |>
  knitr::kable(digits = 3)
```

Read it like this: the condition coefficients shrink from `total` to
`outcome_w_m`, and `perceived_value` is a strong predictor — the mediation
signature.

## Moderation: for whom is the frame weaker?

```{r}
#| label: tbl-moderation
fit_mod <- fit_moderation_model(clean)
broom::tidy(fit_mod, conf.int = TRUE) |>
  dplyr::filter(grepl("condition|price", term)) |>
  knitr::kable(digits = 3)
```

```{r}
#| label: fig-moderation
#| fig-cap: "Condition × price sensitivity. The combined-frame boost shrinks for high-price-sensitive shoppers."
#| fig-width: 7
#| fig-height: 4
plot_moderation(clean)
```

## What got reused, not copied

Every result on this page came from somewhere shared:

| On this page | Defined in |
| --- | --- |
| `fit_main_model()`, `fit_mediation_models()`, `fit_moderation_model()` | [`R/functions/analysis.R`](https://github.com/TheDataFlowCompany/the-science-repository/blob/main/R/functions/analysis.R) |
| `plot_moderation()` and the other plots | [`R/functions/plotting.R`](https://github.com/TheDataFlowCompany/the-science-repository/blob/main/R/functions/plotting.R) |
| The cleaned data | written by [page 1](01-data-preparation.qmd), read here |
| Citations `[@baron1986]` | [`references/references.bib`](https://github.com/TheDataFlowCompany/the-science-repository/blob/main/references/references.bib) |

Rename `purchase_intention` in `R/01_setup.R` and `R/functions/data_loading.R`
— two files — and this website and the manuscript all follow.

## References

::: {#refs}
:::
