---
title: "A first reproducible report"
subtitle: "Day 2 · Pt. 4 — code, prose, and results in one document"
date: today
format:
  html:
    toc: true
    code-fold: show
    embed-resources: true
    theme: cosmo
execute:
  warning: false
  message: false
---

```{r setup}
#| include: false
# This chunk runs first and is hidden from the page (include: false).
#
# A report needs to find the project's files, but it renders from its OWN
# folder, so here::here() would stop too early. Instead we anchor on the git
# root — the top of the repository — and build every path from there. This is
# the exact same line the real project pages use; look at the top of
# reports/webpage/01-data-preparation.qmd and you will recognise it.
root <- rprojroot::find_root(rprojroot::is_git_root)

library(dplyr)
library(ggplot2)

# Load our engine (Act 3) and the raw teaching data, anchored at the repo root.
source(file.path(root, "workshop", "materials", "day_2", "03_functions.R"))
raw   <- readr::read_csv(
  file.path(root, "data", "mock", "consumer_data_raw.csv"),
  show_col_types = FALSE
)
clean <- clean_consumer(raw)

# Two vectors we'll report on inline, in prose, further down.
pi_all      <- clean$purchase_intention
pi_combined <- clean$purchase_intention[clean$condition == "combined_frame"]
```

## What a Quarto report is

This document is a `.qmd` file: ordinary prose (like this sentence) interleaved
with **code chunks** that R runs when the document is *rendered*. The output —
tables, figures, numbers — is dropped straight into the page. Nothing is
copy-pasted from the Console, so the report can never drift out of sync with the
analysis. Re-render it and every number updates itself.

A chunk is fenced like this and shows both the code and its result (click
**Code** to fold or unfold it):

```{r}
1 + 1
```

## The data

We read the same 300-participant teaching dataset as the scripts, and clean it
with `clean_consumer()` — the function we defined in
`03_functions.R`. The report does not *re-implement* the cleaning; it *reuses*
it. One source of truth.

```{r}
glimpse(select(clean, participant_id, condition, age, purchase_intention))
```

## Does the message frame move purchase intention?

`pi_by_condition()` summarises the outcome by experimental condition.
`knitr::kable()` turns the resulting data frame into a proper table.

```{r}
#| label: tbl-pi
#| tbl-cap: "Mean purchase intention (1–7) by message frame."
knitr::kable(pi_by_condition(clean), digits = 2)
```

The `combined_frame` row stands out. Across all `r nrow(clean)` shoppers,
purchase intention sat just above the midpoint of the 1–7 scale
(`r apa_msd(pi_all)`), and it was highest in the combined-frame condition
(`r apa_msd(pi_combined)`).

Those statistics are **computed, not typed**. The second one is written in the
source as the inline expression `r knitr::inline_expr("apa_msd(pi_combined)")`,
which calls `apa_msd()` from the engine in `03_functions.R` and formats the mean
and SD in APA 7th-edition style (italic *M* and *SD*). Change the data and
re-render, and the sentence updates itself — the prose can never drift out of
step with the analysis. A figure makes the spread behind those means visible:

```{r}
#| label: fig-pi
#| fig-cap: "Purchase intention by message frame."
#| fig-width: 7
#| fig-height: 4
plot_pi(clean)
```

## Where this goes next

You have now seen the whole arc in miniature: **console → script → functions →
report**. The pattern in this one file — *source the shared engine, call its
functions, narrate the result* — is exactly how the project's website is built.

This afternoon you will work inside the full version of it:

- the engine lives in [`R/01_setup.R`](../../../R/01_setup.R) and
  [`R/functions/`](../../../R/functions/);
- the report pages live in
  [`reports/webpage/`](../../../reports/webpage/) — open
  `01-data-preparation.qmd` and you will see the grown-up twin of this file.

Render this document yourself from the project root with:

```bash
quarto render workshop/materials/day_2/05_report.qmd
```

The HTML lands next to the `.qmd`. Open it in a browser — that is a complete,
reproducible report built from nothing but code.
